### 2019-06-10 thesis-template/msc-thesis.tex
update

\section{Light Propagation Scheme Behaviour}
To evaluate the plausibility of the light distribution results obtained from the light propagation scheme, we plot the transmission profiles overlaid with the resulting intensity profiles for several synthetic test fields:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/isotropic.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/isotropic-all-center.png}
    \label{b)}
  \end{minipage}
\caption{a) tensor field Lines and glyphs for ``rings''-Testfield, b) intensity propagation in grid}
\label{anisotropy}
\end{figure}

>>>>

\section{Light Propagation Scheme Behaviour}
To evaluate the plausibility of the light distribution results obtained from the light propagation scheme, we plot the transmission profiles overlaid with the resulting intensity profiles for several synthetic test fields:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/isotropic.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/isotropic-all-center.png}
    \label{b)}
  \end{minipage}
\caption{final light propagation distributions for ``isotropy''-testfield}
\label{isotropic}
\end{figure}

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/rings-two-special1.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/rings-two-special2.png}
    \label{b)}
  \end{minipage}
\caption{final light propagation distributions for ``rings''-testfield}
\label{rings-tests}
\end{figure}

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/spiral-two-dense.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/spiral-two-wide.png}
    \label{b)}
  \end{minipage}
\caption{final light propagation distributions for ``spiral''-testfield}
\label{spiral-tests}
\end{figure}

\begin{figure}[!t]
\centering
  \begin{minipage}{0.33\textwidth}
    \includegraphics[width=\textwidth]{img/star-0,0.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.33\textwidth}
    \includegraphics[width=\textwidth]{img/star-two-dense.png}
    \label{b)}
  \end{minipage}
   \begin{minipage}{0.33\textwidth}
    \includegraphics[width=\textwidth]{img/star-two-wide.png}
    \label{c)}
  \end{minipage}
\caption{final light propagation distributions for ``star''-testfield}
\label{spiral-tests}
\end{figure}
